### 2015-04-15 paper/main.tex
automate table generation

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

@@

Interestingly, even in the ``bimodal" scenario where the UA is severely contradicted, the estimated $g$ from $\ashr$ 
is visually more accurate than that from mixFdr: although mixFdr is capable, in principle, of fitting the multiple modes of $g$, it does not do this well here. We believe this
is mostly because the noise level is sufficiently large to make reliable estimation of the multiple modes difficult, rather than reflecting
deficiencies in the specific choices made by mixFdr, and indeed in simulations where the modes are sufficiently well-spaced
to be clearly visible in the observed $\betahat$, mixFdr is able to fit this modes (Supplementary Information; 
\url{dsc-shrink/check_mixfdr_lownoise.rmd}). Of course, we would not advocate the UA in settings where multi-modality is 
clearly visible in the observed $\betahat$.

@@

>>>>

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}
\usepackage{caption}
\usepackage{subcaption}

@@

Interestingly, even in the ``bimodal" scenario where the UA is severely contradicted, the estimated $g$ from $\ashr$ 
is visually more accurate than that from mixFdr: although mixFdr is capable, in principle, of fitting the multiple modes of $g$, it does not do this well here. We believe this
mostly reflects the fact that the noise level is sufficiently large to make reliable estimation of the multiple modes difficult, rather than 
fundamental deficiencies of mixFdr. Indeed, in multi-modal simulations where the multiple modes are sufficiently well-spaced
to be clearly visible in the observed $\bhat$, mixFdr fits these modes (Supplementary Information; 
\url{dsc-shrink/check_mixfdr_lownoise.rmd}). Of course, we would not advocate the UA in settings where multi-modality is 
clearly visible in the observed $\bhat$.

@@

\begin{table}[!ht]
\begin{subtable}{\textwidth}
	\input{tables/coverage_all.tex}
	\caption{All}
\end{subtable}

\begin{subtable}{\textwidth}
\input{tables/coverage_neg.tex}
\caption{Negative findings}
\end{subtable}

\begin{subtable}{\textwidth}
\input{tables/coverage_pos.tex}
\caption{Positive findings}
\end{subtable}

\caption{Table of 5\% lower tail coverage rates by scenario and method}
\end{table}
